---
title: "Classification"
subtitle: "classification"
author: "Alireza Darvishi"
date: "`r Sys.time()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: null
---


# Loading data and packages
```{r loading data and packages, message=FALSE, warning=FALSE}
library(readxl)
library(tidyverse)
library(glmnet)
library(verification)
library(MASS)
data <- read_excel("default of credit card clients.xls")
head(data)
```
# Data description
This research employed a binary variable, default payment (Yes = 1, No = 0), as the response variable. This study used the following 23 variables as explanatory variables

Amount of the given credit (NT dollar): it includes both the individual consumer credit and his/her family (supplementary) credit.

Gender (1 = male; 2 = female). 

Education (0 = unknown; 1 = graduate school; 2 = university; 3 = high school; 4 = others). 

Marital status (0 = unknown; 1 = married; 2 = single; 3 = others). 

Age (year).

PAY_1 - PAY_6 : History of past payment. We tracked the past monthly payment records (from April to September, 2005) as follows: PAY_1 = the repayment status in September, 2005; PAY_2 = the repayment status in August, 2005; . . .;PAY_6 = the repayment status in April, 2005. The measurement scale for the repayment status is: -1 = pay duly; 1 = payment delay for one month; 2 = payment delay for two months; . . .; 8 = payment delay for eight months; 9 = payment delay for nine months and above. 

Amount of bill statement (NT dollar). BIL_AMT1 = amount of bill statement in September, 2005; BIL_AMT2 = amount of bill statement in August, 2005; . . .; BIL_AMT6 = amount of bill statement in April, 2005. 

Amount of previous payment (NT dollar). PAY_AMT1 = amount paid in September, 2005; PAY_AMT2 = amount paid in August, 2005; . . .;PAY_AMT6 = amount paid in April, 2005. 

## Preprocess and data summary

```{r preprocces and data summary, warning=FALSE}
data$SEX = as.factor(data$SEX)
data$EDUCATION = as.factor(data$EDUCATION)
data$MARRIAGE = as.factor(data$MARRIAGE)
data$def_pymnt_nxt_mnth = as.factor(data$def_pymnt_nxt_mnth)
summary(data[,-1])
```
# Visualization

```{r visualization, warning=FALSE}
ggplot(data) +
  geom_histogram(
    aes(x=AGE,fill = SEX),
    bins = 30)
ggplot(data) +
  geom_boxplot(
    aes(y=LIMIT_BAL,
        color = MARRIAGE , x = MARRIAGE))
ggplot(data) +
  geom_point(
    aes(color = SEX ,
        y=LIMIT_BAL,
        x = (BILL_AMT1+BILL_AMT2+BILL_AMT3+
               BILL_AMT4+BILL_AMT5+BILL_AMT6)))
ggplot(data) +
  geom_boxplot(
    aes(y=LIMIT_BAL,
        color = def_pymnt_nxt_mnth ,
        x = def_pymnt_nxt_mnth))
ggplot(data) +
  geom_histogram(
    aes(fill = def_pymnt_nxt_mnth ,
        x = LIMIT_BAL),bins=25)
```

# Data manipulation

```{r corelation}
data = na.omit(data)
cor(data[,7:12])
cor(data[,13:18])
cor(data[,19:24])
```

As we can see PAYs are correlated with each other and BILLs are correlated with each other as well.

So we summarise these data to lower dimension using linear transformations below.

But PAY_AMTs are not correlated so we keep theme and regularize it with credit limit value. 

```{r data manipulation}
data %>% mutate(PAY_AMT_SUM=
                  PAY_1*PAY_AMT1+PAY_2*PAY_AMT2+
                  PAY_3*PAY_AMT3+PAY_4*PAY_AMT4+
                  PAY_5*PAY_AMT5+PAY_6*PAY_AMT6 ,
                REGULARIZED_BILL = 
                  PAY_1*BILL_AMT1 +PAY_2*BILL_AMT2 +
                  PAY_3*BILL_AMT3 +PAY_4*BILL_AMT4 +
                  PAY_5*BILL_AMT5 +PAY_6*BILL_AMT6 ,
                PAY_MEAN = PAY_1/6+PAY_2/6+PAY_3/6+
                  PAY_4/6+PAY_5/6+PAY_6/6 ,
                PAY_RATIO1 = PAY_AMT1/LIMIT_BAL ,
                PAY_RATIO2 = PAY_AMT2/LIMIT_BAL ,
                PAY_RATIO3 = PAY_AMT3/LIMIT_BAL ,
                PAY_RATIO4 = PAY_AMT4/LIMIT_BAL ,
                PAY_RATIO5 = PAY_AMT5/LIMIT_BAL ,
                PAY_RATIO6 = PAY_AMT6/LIMIT_BAL ) %>% .[-c(7:24,1)] -> new_data
train_idx = sample(30000,size = 0.8*30000)
train_data = new_data[train_idx,]
test_data = new_data[-train_idx,]
x = model.matrix(def_pymnt_nxt_mnth~., train_data)[,-1]
y <- ifelse(train_data$def_pymnt_nxt_mnth == 1, 1, 0)
x.test <- model.matrix(def_pymnt_nxt_mnth ~., test_data)[,-1]
y.test = ifelse(test_data$def_pymnt_nxt_mnth == 1, 1, 0)
```
# Model selection
This data set has 15 demension so KNN is not a proper model.

In this section we fit Logistic Regression and LDA:

## Logistic Regression with lasso:
```{r LR with Lasso, warning=FALSE}
cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")
plot(cv.lasso)
LR.Lasso_model <- glmnet(x, y, alpha = 1, family = "binomial",
                lambda = cv.lasso$lambda.min)
pred.lr = predict(LR.Lasso_model,newx = x.test,type = "response")
roc.plot(y.test,pred.lr)
thresh = 0.35
table(pred.lr>thresh,y.test)
mean((pred.lr>thresh) == y.test)
#roc_data = roc.glmnet(model,newx = x.test,newy = y.test, family = "binomial")
#ggplot(roc_data) + geom_line(aes(x= FPR,y=TPR)) + geom_abline(slope = 1)
```
## Logistic Regression with ridge:
```{r LR with Ridge, warning=FALSE}
cv.ridge <- cv.glmnet(x, y, alpha = 0, family = "binomial")
plot(cv.ridge)
LR.ridge_model <- glmnet(x, y, alpha = 0, family = "binomial",
                lambda = cv.ridge$lambda.min)
pred.lr = predict(LR.ridge_model,newx = x.test,type = "response")
roc.plot(y.test,pred.lr)
thresh = 0.35
table(pred.lr>thresh,y.test)
mean((pred.lr>thresh) == y.test)
#roc_data = roc.glmnet(model,newx = x.test,newy = y.test, family = "binomial")
#ggplot(roc_data) + geom_line(aes(x= FPR,y=TPR)) + geom_abline(slope = 1)
```
## LDA:
```{r LDA, warning=FALSE}
lda.fit = lda(data = new_data , subset = train_idx , def_pymnt_nxt_mnth~.)
roc.plot(y.test,predict(lda.fit,newdata = test_data)$posterior[,2])
pred.lda = predict(lda.fit,newdata = test_data)$class
table(pred.lda,y.test)
mean(pred.lda == y.test)
```
# Final results
Comparing result of these models, Logestic reggresion with lasso is slightly better than other models.

Final Coefs are reported below:

```{r warning=FALSE}
coef(LR.Lasso_model)
```


