---
title: "HW3-Q3"
author: "Alireza Darvishi-96109674"
date: "`r Sys.time()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: null
---
<font face="Chalkboard">
a)
</font>

<font face="Times New Roman">
loading data and libreries
</font>

```{r message=FALSE, warning=FALSE}
library(readxl)
library(ggplot2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(broom)
read_xls(path = "../edu.xls") -> edu

```
<font face="Chalkboard">
b)
</font>

<font face="Times New Roman">
dummy variables: female , black , hispanic , dadcol , momcoll , ownhome , urban , incomehi
</font>

<font face="Chalkboard">
c)
</font>

```{r}
ggplot(data=edu,aes(x=bytest,y=ed,color=as.factor(black)))+geom_point()+
  geom_smooth(method = "lm",aes(group=black))
```

<font face="Chalkboard">
d)
</font>

```{r}
ggplot(data=edu,aes(x=bytest,y=ed,color=as.factor(female)))+
  geom_point()+geom_smooth(method = "lm")
```
<font face="Chalkboard">
e)
</font>

```{r}
ggplot(data=edu,aes(x=bytest,y=ed,colour=as.factor(momcoll):as.factor(dadcoll)))+
  geom_point()+geom_smooth(method = "lm")
```
<font face="Chalkboard">
f)
</font>

```{r}
edu$female=as.factor(edu$female)
edu$black=as.factor(edu$black)
edu$hispanic=as.factor(edu$hispanic)
edu$dadcoll=as.factor(edu$dadcoll)
edu$momcoll=as.factor(edu$momcoll)
edu$ownhome=as.factor(edu$ownhome)
edu$urban=as.factor(edu$urban)
edu$incomehi=as.factor(edu$incomehi)
```

<font face="Chalkboard">
g)
</font>

```{r}
linear_model=lm(data=edu , formula = ed ~ .)
summary(linear_model)
```
<font face="Chalkboard">
h)
</font>

<font face="Times New Roman">
female1: females had more education years
black1: black peaple had more education years
hispanic1: hispanic peaple had more education years
bytest: a pearson with more score in Base Year Composite Test had more education
dadcoll1: a person whose his father went to college had more education years
momcoll1: a person whose his father went to college had more education years
ownhome1: a pearson with home has more education years
other coefs are like those mentioned above
it's logical that momcoll1 , dadcoll1 and incomehi1 coefs are positive. also bytest is positive.

</font>

<font face="Chalkboard">
i)
</font>
```{r}
residuals_data=cbind(abs_resud=abs(linear_model$residuals),edu)
res_model=lm(data=residuals_data , formula = abs_resud~ed)
ggplot(data=residuals_data,aes(x=ed,y=abs_resud))+geom_point()+geom_smooth(method = "lm")
plot(res_model)
```
<font face="Times New Roman">
absolute of residuals are correlated with ed and so model is not valid.

</font>

<font face="Chalkboard">
j)
</font>
```{r}
edu$dist_less_than_10=as.factor(edu$dist<=1)
edu %>% group_by(dist_less_than_10) %>% nest() %>% mutate ( lm_fit = map ( data , ~lm( data=. ,formula = ed~.) ), results = map(lm_fit, glance) ) %>% unnest(results) %>%  .$lm_fit


```

