---
title: "HW3-Q2"
author: "Alireza Darvishi-96109674"
date: "`r Sys.time()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: null
---

laoding data

```{r}
library(ISLR)
attach(Carseats)
head(Carseats)
```
<font face="Chalkboard">
a)
</font>
```{r}
linear_model=lm(Carseats,formula = Sales~Price+Urban+US)
summary(linear_model)
```
<font face="Chalkboard">
b)<br>
</font>

<font face="Times New Roman">
price coef: Sales deacreas 0.05 unit with 1 unit increase in price <br>
USYes coef: diffrence of Sales for two same Carseats one sold in US and one sold out of US and all other variables are same <br>
UrbanYes coef: diffrence of Sales for two same Carseats one sold in Urban and one sold in rural and all other variables are same <br>
</font>

<font face="Chalkboard">
c)<br>
</font>
$Sales = \beta_0+\beta_1 Price+\beta_2 UrbanYes +\beta_3 USYes$<br>
<font face="Chalkboard">
d)<br>
</font>
UrbanYes coef p-value is 0.936 so we can't reject hypothesis $\beta_2=0$<br>
<font face="Chalkboard">
e)
</font>
```{r}
linear_model=lm(Carseats,formula = Sales~Price+US)
summary(linear_model)
```
<font face="Chalkboard">
f)
</font>

model a adjusted R-squard=0.2335

model e adjusted R-squard=0.2354

<font face="Chalkboard">
g)
</font>
```{r}
confint(linear_model,level = 0.95)
```
<font face="Chalkboard">
h)
</font>
```{r}
plot(linear_model,which = c(5))
```

